The \textit{Kepler} Smear Campaign

### 2019-03-20 paper/ms.tex
mistake

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}. No diffusion or rotational mixing was included, while core overshoot with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}.

>>>>

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}. The isochrones include core overshooting with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}, but do not include diffusion or rotational mixing.
